Manuscript analyses

### 2024-04-20 cilta_cel/Manuscript analyses.Rmd
Add variable and update figures

  mutate(across(c(starts_with("marrow_dysplasia_") & ends_with("yes_no")), ~ case_when(
    . == "0"                                ~ "No",
    . == "1"                                ~ "Yes",
    TRUE                                    ~ .
  )))

@@

                         bm_plasma_cell_percent_at_pre_ld = "Circulating Plasma Cells?",

@@

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) %>% as_gt() #%>%
  # gt::tab_source_note(gt::md("**At 30days: <br>
  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
  #                            1 patients was not evaluated. <br>
  #                            At 90days: <br>
  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
  #                            1 patient is not Heme not evaluable; <br>
  #                            2 patients were not evaluated; <br>
  #                            1 patients is not evaluable by death**"))

@@

tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
                          "Day 7", "Day 14", "Day 21",
                          "Day 30", "Day 90", "Day 180")) %>% as_gt() #%>%
# gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
#                            1 patient has missing 90 days values**"))
```

@@

## Table S4a. Patient characteristics by grade 3+ cytopenia at Day 30
```{r Patient characteristics by grade 3+ cytopenia at Day 30}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
  select(bm_plasma_cell_percent_at_pre_ld,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
         os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         gr3_cytopenia_30d) %>% 
  tbl_summary(by = gr3_cytopenia_30d,
              type = list(
                c(extramedullary_disease_yes_no,
                  bm_plasma_cell_percent_at_pre_ld,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  Prior_bcma_therapy,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~"categorical",
                c(bm_plasma_cell_percent_at_pre_ld,
                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
```

## Table S4b. Patient characteristics by ANY early ICAHT
```{r Patient characteristics by grade 3+ early ICAHT}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
  select(bm_plasma_cell_percent_at_pre_ld,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
         os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         any_early_icaht) %>% 
  tbl_summary(by = any_early_icaht,
              type = list(
                c(extramedullary_disease_yes_no,
                  bm_plasma_cell_percent_at_pre_ld,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  Prior_bcma_therapy,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~"categorical",
                c(bm_plasma_cell_percent_at_pre_ld,
                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Early ICAHT**")
```

## Table S5a. Patient characteristics by grade 3+ cytopenia at Day 90
```{r Patient characteristics by grade 3+ cytopenia at Day 90}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
  select(bm_plasma_cell_percent_at_pre_ld,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
         os_from_infusion_months,
         age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         gr3_cytopenia_90d) %>% 
  tbl_summary(by = gr3_cytopenia_90d,
              type = list(
                c(extramedullary_disease_yes_no,
                  bm_plasma_cell_percent_at_pre_ld,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~ "categorical",
                c(bm_plasma_cell_percent_at_pre_ld,
                  number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
```

>>>>

  mutate(across(c(starts_with("marrow_dysplasia_") & ends_with("yes_no")), ~ case_when(
    . == "0"                                ~ "No",
    . == "1"                                ~ "Yes",
    TRUE                                    ~ .
  ))) %>% 
  mutate(circulating_plasma_cell = case_when(
    plasmacytes_day_5_percent == 0          ~ "0",
    plasmacytes_day_5_percent > 0           ~ "> 0",
  ), circulating_plasma_cell = factor(circulating_plasma_cell, 
                                      levels = c("0", "> 0")))

@@

                         circulating_plasma_cell = "UPDATED Circulating Plasma Cells",

@@

tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8)) #%>% as_gt() #%>%
  # gt::tab_source_note(gt::md("**At 30days: <br>
  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
  #                            1 patients was not evaluated. <br>
  #                            At 90days: <br>
  #                            1 patient is not evaluable by IMWG - non-secretory disease, including no bone marrow involvement; <br>
  #                            1 patient is not Heme not evaluable; <br>
  #                            2 patients were not evaluated; <br>
  #                            1 patients is not evaluable by death**"))

@@

tbl_merge(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6, tbl7, tbl8, tbl9), 
          tab_spanner = c("Apheresis", "Day -5", "Day 0", 
                          "Day 7", "Day 14", "Day 21",
                          "Day 30", "Day 90", "Day 180")) # %>% as_gt() #%>%
# gt::tab_source_note(gt::md("**Not evaluable patients are removed from the denominator <br>
#                            1 patient has missing 90 days values**"))
```
<br>

@@

## Table S4a. Patient characteristics by grade 3+ cytopenia at Day 30
```{r Patient characteristics by grade 3+ cytopenia at Day 30}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
  select(circulating_plasma_cell,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
         os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         gr3_cytopenia_30d) %>% 
  tbl_summary(by = gr3_cytopenia_30d,
              type = list(
                c(extramedullary_disease_yes_no,
                  circulating_plasma_cell,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  Prior_bcma_therapy,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~"categorical",
                c(number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 30?**")
```

## Table S4b. Patient characteristics by ANY early ICAHT
```{r Patient characteristics by grade 3+ early ICAHT}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_30days)) %>% ######################### Fix evaluable----------
  select(circulating_plasma_cell,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,         ################# Not in data?
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day30" = marrow_percent_cellularity_day_30,
         os_from_infusion_months, age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, 
         r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         any_early_icaht) %>% 
  tbl_summary(by = any_early_icaht,
              type = list(
                c(extramedullary_disease_yes_no,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  Prior_bcma_therapy,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~"categorical",
                c(number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day30`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>% add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Early ICAHT**")
```

## Table S5a. Patient characteristics by grade 3+ cytopenia at Day 90
```{r Patient characteristics by grade 3+ cytopenia at Day 90}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
  select(circulating_plasma_cell,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
         os_from_infusion_months,
         age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         gr3_cytopenia_90d) %>% 
  tbl_summary(by = gr3_cytopenia_90d,
              type = list(
                c(extramedullary_disease_yes_no,
                  circulating_plasma_cell,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~ "categorical",
                c(number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
```

## Table S5b. Patient characteristics by ANY late ICAHT
```{r Patient characteristics by grade 3+ late ICAHT}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  # filter(is.na(Not_evaluable_at_90days)) %>%  ######################### Fix evaluable----------
  select(circulating_plasma_cell,
         number_of_prior_lines_of_therapy,
         number_prior_lines_therapy,
         # `Days from last bridging to CAR-T infusion`,
         lenalidomide_exposed_vs_refractory_vs_not_exposed,
         bortezomib_exposed_vs_refractory_vs_not_exposed,
         carfilzomib_exposed_vs_refractory_vs_not_exposed,
         pomalidomide_exposed_vs_refractory_vs_not_exposed,
         # daratumumab_or_isatuximab_cd38_m_ab_exposed_vs_refractory_vs_not_exposed,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         "Marrow Cellularity (%) at Day90" = marrow_percent_cellularity_day_90,
         os_from_infusion_months,
         age, agecat, male_sex, sex,
         extramedullary_disease_yes_no, 
         high_marrow_burden_50_percent, ecog_at_ld, r_iss_at_car_t_infusion, 
         cytogenetics, cytogenetics_incl_1q,
         bridging_therapy_yes_no,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         prior_auto_sct_yes_no, prior_allo_sct_within_6_months_before_apheresis,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         ht_score,
         any_late_icaht) %>% 
  tbl_summary(by = any_late_icaht,
              type = list(
                c(extramedullary_disease_yes_no,
                  circulating_plasma_cell,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cytogenetics, cytogenetics_incl_1q,
                  bridging_therapy_yes_no,
                  # `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  prior_auto_sct_yes_no,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  ht_score,
                  did_patient_meet_eligibility_criteria_for_cartitude_1_on_the_day_of_apheresis_yes_no)
                ~ "categorical",
                c(number_of_prior_lines_of_therapy, `Marrow Cellularity (%) at Day90`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Late ICAHT**")
```
